Probabilistic Symbolic Execution

### 2021-06-23 shared/Paper-Draft/PSE-POPL-2021.tex
WIP : Implementation Section

	We use a robust symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores. For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path. These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the symbolic execution of the program. Apart from \textit{path constraints}, the \textit{state} contains a mapping of \textit{symbolic} variables to \textit{symbolic} expressions or \textit{concrete} values (in the case of concrete execution) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.

	\textsc{KLEE} assigns values to these \textit{symbolic} variables by solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution. Upon reaching a \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to explored next. The process continues untill all the \textit{states} in the \textit{execution} stack are explored.

>>>>

	We use a robust symbolic execution engine, \textsc{KLEE} to generate the \textit{path constraints} corresponding to each path that our tool explores. For each path in the program, \textsc{KLEE} stores a list of \textit{constraints} that encodes the whole path. These constraints are over \textit{program} variables that have been marked \texttt{make\_symbolic()} by the user and are stored in \textsc{KLEE} as \textit{metadata} in the \textit{state} data structure during the \textit{dynamic} symbolic execution of the program.

	\textsc{KLEE} assigns values to these \textit{symbolic} variables by solving the current set of \textit{constraints} seen so far in the program path as described in Algorithm~\ref{alg:symbex} and also by concretizing some of the values that get evaluated as a result of \textit{concrete} execution. Upon reaching the \textit{branch} instruction at Line~\ref{line:branch} in Algorithm~\ref{alg:symbex}, \textsc{KLEE} forks the current \textit{state} by making two identical copies of it and then appending to each of \textit{new} states one additional constraint encoding the \textit{true} and \textit{false} side of the branch and adds it to the \textit{execution} stack containing \textit{states} that need to explored next. The process continues untill all the \textit{states} in the \textit{execution} stack are explored. Apart from \textit{path constraints}, the \textit{state} also contains a mapping of \textit{symbolic} variables to expressions that are either  \textit{symbolic} or \textit{concrete} (in the case of concrete execution of the program) and a list of \textit{instructions} currently getting executed as a part of the \textit{state}.
